Invasive chameleons released from predation display more conspicuous colours

### 2022-02-14 ms_Sci_Adv.Rmd
Adding new Sci Advances formatting

---
title: "Title: Invasive chameleons released from predation display more conspicuous colours"
bibliography: supp_refs.bib
csl: nature.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

**Affiliations**:
^1^ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia

@@

**Acknowledgments**: 
This research was approved by the Kenya Wildlife Service (R. Bagine, KWS 5001) and Ministry of Science & Technology (Research Permit No. MOS&T 13/36C 208). Financial support was provided by the University of the Witwatersrand to MJW. We thank Idle Farah and Patrick Malonza of the National Museums of Kenya for facilitating the research, Joseph Gathua for amazing field support and Jan Stipala for use of his field vehicle. We thank the Ditsong National Museum of Natural History (formerly Transvaal Museum) for the stuffed African Cuckoo Hawk. Ben Phillips, Rick Shine and Tobias Uller provided feedback on earlier drafts of this manuscript. We thank Fonti Kar for help curating data and Drew Allen for statistical advice.

>>>>

---
title: "Title: Invasive chameleons released from predation display more conspicuous colours"
bibliography: supp_refs.bib
csl: science-advances.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

@@

**Affiliations**:
^1^ School of Natural Sciences, Macquarie University, Sydney, NSW 2109, Australia; martin.whiting@mq.edu.au

@@

[@RN1; @RN2; @RN3; @RN4; @RN5]
**Acknowledgments**: 
This research was approved by the Kenya Wildlife Service (R. Bagine, KWS 5001) and Ministry of Science & Technology (Research Permit No. MOS&T 13/36C 208). Financial support was provided by the University of the Witwatersrand to MJW. We thank Idle Farah and Patrick Malonza of the National Museums of Kenya for facilitating the research, Joseph Gathua for amazing field support and Jan Stipala for use of his field vehicle. We thank the Ditsong National Museum of Natural History (formerly Transvaal Museum) for the stuffed African Cuckoo Hawk. Ben Phillips, Rick Shine and Tobias Uller provided feedback on earlier drafts of this manuscript. We thank Fonti Kar for help curating data and Drew Allen for statistical advice.

### 2022-02-14 supp_Sci_Adv.Rmd
Adding new Sci Advances formatting

---
title: "Invasive chameleons released from predation display more conspicuous colours"
date: "`r Sys.Date()`"
bibliography: supp_refs.bib
csl: nature.csl
output: 
  bookdown::word_document2:
    toc: no
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
---
```{r setup, include=FALSE, purl = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE)
## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits      ## and rounded to 2 digits
  options(digits = 2)
```

@@

>>>>

---
title: "Invasive chameleons released from predation display more conspicuous colours"
date: "`r Sys.Date()`"
bibliography: supp_refs.bib
csl: science-advances.csl
output: 
  bookdown::word_document2:
    toc: no
    number_sections: false
    reference_docx: template.docx
---
```{r setup, include=FALSE, purl = FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE)
## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits      ## and rounded to 2 digits
  options(digits = 2)
```

@@

**The file includes**:
\n Supplementary text
\n Figures S1 – S9
\n Tables S1 – S14
\n References 1-5
